Bayesian inference of relative fitness on high-throughput pooled competition assays

### 2023-12-05 doc/_hierarchical_replicates_results.qmd
add text color based on reviews

Our inference pipeline can be extended to account for multiple experimental
replicates via Bayesian hierarchical models [@betancourt2013]. Briefly, when
accounting for multiple repeated measurements of the same phenomena, there are
two extreme cases one can use to perform the data analysis: On the one hand, we
can treat each measurement as entirely independent, losing the power to utilize
multiple measurements when trying to learn a single parameter. This can
negatively impact the inference since, in principle, the value of our parameter
of interest should not depend on the particular experimental replicate in
question. However, this approach does not allow us to properly "combine" the
uncertainties in both experiments when performing the inference. On the other
hand, we can pool all data together and treat our different experiments as a
single measurement with higher coverage. This loses the subtle differences due
to biotic and abiotic batch effects, effectively halving the data that goes into
our inference problem.

>>>>

Our inference pipeline can be extended to account for multiple experimental
replicates via Bayesian hierarchical models [@betancourt2013]. Briefly, when
accounting for multiple repeated measurements of the same phenomena, there are
two extreme cases one can use to perform the data analysis: On the one hand, we
can treat each measurement as entirely independent, losing the power to utilize
multiple measurements when trying to learn a single parameter. This can
negatively impact the inference since, in principle, the value of our parameter
of interest should not depend on the particular experimental replicate in
question. However, this approach does not allow us to properly "combine" the
uncertainties in both experiments when performing the inference. On the other
hand, we can pool all data together and treat our different experiments as a
single measurement with higher coverage. 
<span style="color: #912E27;">
However, by doing so, we lose all information about experiment-to-experiment
variability due to intrinsic biological variability and environmental
fluctuations---such as small temperature fluctuations---that we cannot control.
In this sense, combining the datasets defeats the purpose of performing multiple
measurements to account for this variability when extracting the relevant
information from the observations.
</span>
